---
title: "Part 1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
```
## Data Preprocessing

### Load Data
```{r}
df <- read.csv("BankChurners.csv")
```

### Retain Existing Customer
Since we are only interested in the customers who has "healthy" relationship with the bank, 
```{r}
df <- df[df$Attrition_Flag == "Existing Customer", ]
```

### Remove Unknown values
```{r}
df <- df[df$Income_Category != "Unknown", ]
df <- df[df$Education_Level != "Unknown", ]
df <- df[df$Marital_Status != "Unknown", ]
```

### Retain Variables of Interest
```{r}
variables = c("Credit_Limit", "Income_Category", "Customer_Age", "Total_Trans_Ct", "Months_on_book", "Gender", "Education_Level", "Marital_Status")
df <- df[variables]
```


```{r}
df
```
### Generate Summary of All Variables

```{r}
summary(df)
```
### Generate Summary of Categorical Variables
```{r}
n = count(df)
table(df$Education_Level) / dim(df)[1]
```

## Fit Linear Model

```{r}
mdl = lm(Credit_Limit ~ Income_Category + Customer_Age + Total_Trans_Ct + Months_on_book + Gender + Education_Level + Marital_Status, data=df)
```

```{r}
summary(mdl)
```

## Checking Assumptions

# Retrieve data of interest
```{r}
e_hat = resid(mdl)
y_hat = fitted(mdl)
y = df$Credit_Limit
```


### Plot 1: Residuals vs. Fitted
```{r}
plot(x = y_hat, y = e_hat, main = "Residuals vs. Fitted", ylab = "Residuals", xlab ="Fitted")
```
### Plot 2: Residuals vs. Predictors

```{r}
num_vars = c("Customer_Age", "Total_Trans_Ct", "Months_on_book")
cat_vars = c("Income_Category", "Gender", "Education_Level", "Marital_Status")
```

#### Plot Numerical Variables
```{r}
par(mfrow=c(2, 2))
for (var in num_vars) {
  plot(e_hat ~ as.vector(unlist(df[var])), main = paste("Residuals vs. ", var), ylab = "Residuals", xlab =var)
}
```

#### Plot Categorical Variables
```{r}
par(mfrow=c(2, 2))
for (var in cat_vars) {
  names = names(table(df[var]))
  boxplot(e_hat ~ as.vector(unlist(df[var])), main = paste("Residuals vs. ", var), ylab = "Residuals", xlab =var, names=names)
}
```

Note that in the box plot of residuals vs. Income_Category and Education_Level, some category label is missing due to limited space (which is automatic), so we will state it here for reference:

- For Income_Category, the missing label is "Less than $40K",
- For Education_Level, the missing labels are "High School" (on the left) and "Uneducated" (on the right).

### Plot 3: QQ plot for Residuals
```{r}
qqnorm(e_hat)
qqline(e_hat)
```

### Plot 4: Response vs. Fitted
```{r}
plot(x = y_hat, y = df$Credit_Limit, main = "Response vs. Fitted", ylab = "Response", xlab ="Fitted")
abline(a = 0,b = 1, lty=2, col = "red")
```

### Plot 5: Pairwise Scatterplot of Predictors

#### Relationship Between Numerical Variables
```{r}
pairs(df[num_vars])
```

#### Relationship between Numerical and Categorical Variables
```{r}
plot_boxplot <- function(df, num_var, cat_var) {
  numeric_lists <- split(df[[num_var]], df[[cat_var]])
  
  # Create a side-by-side boxplot
  boxplot(numeric_lists,
          names = names(numeric_lists),
          main = paste(cat_var, " vs. ", num_var),
          xlab = cat_var,
          ylab = num_var
          )
}
```

```{r}
counter = 0
par(mfrow = c(2, 3))
for (cat_var in cat_vars){
  
  for (num_var in num_vars) {
    plot_boxplot(df, num_var, cat_var)
  }
  counter = counter + 1
  if (counter == 2){
    par(mfrow = c(2, 3))
  }
}
```
Note that the missing x label in Income_Category and Education_Level are due to the same reason mentioned above.



























